Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-21 demystify.tex
updates

\begin{commentbox}[Thanh:]
    Due to academic culture, professors in Vietnam usually aim for (international) journals instead of conferences. Could you give some tips on how to know whether a journal is good (CSrankings, unfortunately, only consider conferences)?
    \tcblower
    \textbf{Vu}: One way is looking at what well-known researchers publish. For example, if you are interested in a field X, you can use CSRankings to look at active faculty in X, and then look at their websites to see what journals they publish at.
\end{commentbox}
\paragraph{What if I don't have any pubs} It is understandable that many students do not have the opportunity to publish papers. Thus, other writings, even those under submissions or rejected, would still be good and better than nothing.  Be sure to upload your papers with your application and talk about them in your statement (see \autoref{chap:sop}).

@@

\begin{commentbox}[Craig:]
  Mason and many other universities allow you to upload your published papers and other writing samples. In many cases, even if the papers were not published at top places, we can still determine their quality by simply skimming over the paper.
\end{commentbox}

@@

\section{Writing Sample}\label{sec:writing-sample}
TBD TODO

@@

    \item \textbf{Too long}. Keep it to about 3--4 short paragraphs. Less is more and too long emails are often not read and discarded. Don't attach course transcript or test scores in the first email. If they are  interested they will ask for them.  Attaching CV is OK. Sample papers and links to your Arxiv papers or GitHub projects are also OK if they are relevant.

>>>>

\begin{commentbox}[Thanh:]
    Due to academic culture, professors in Vietnam usually aim for (international) journals instead of conferences. Could you give some tips on how to know whether a journal is good (CSrankings, unfortunately, only consider conferences)?
    \tcblower
    \textbf{Vu}: One way is looking at what well-known researchers publish. For example, if you are interested in a field X, you can use CSRankings to look at active faculty in X, and then look at their websites to see what journals they publish at.
\end{commentbox}
\paragraph{What if I don't have any pubs} It is understandable that many students do not have the opportunity to publish papers. Thus, other writings, even those under submissions or rejected, would still be good and better than nothing.  Be sure to upload your papers with your application (\autoref{sec:writing-sample}) and talk about them in your SOP (\autoref{chap:sop}).

@@

\begin{commentbox}[Craig:]
  Mason and many other universities allow you to upload your published papers and other writing samples (\autoref{sec:writing-sample}). In many cases, even if the papers were not published at top places, we can still determine their quality by simply skimming over the paper.
\end{commentbox}

@@

\section{Writing Sample}\label{sec:writing-sample}
It is a good idea to upload a writing sample, e.g., a paper you wrote, a report, or a thesis.  Even if the paper is published, not published, or already on Arxiv, you should upload it. Because samples are part of the application package, adcom members can quickly skim through it to see your research and writing abilities.

@@

    \item \textbf{Too long}. Keep it to about 3--4 short paragraphs. Less is more and too long emails are often not read and discarded. Don't attach course transcript or test scores in the first email. If they are  interested they will ask for them.  Attaching CV is OK. Sample papers (\autoref{sec:writing-sample}) and links to your Arxiv papers or GitHub projects are also OK if they are relevant.
